### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@4dfeb7848376a8e014f73bc4f73aa468a2264cde 🚀

\begin{itemize}
\tightlist
\item
  We estimate the Colorado bumblebee/wild-flower pollination metaweb
  using network embedding.
\item
  Then decompose into spatial and temporally explicit network
  predictions
\item
  Finally suggest a priority of sampling to improve our understanding of
  this system.
\end{itemize}

@@

@@

\textbf{\emph{Figure 2: Model Fit Figure}}
\includegraphics{./figures/PR_ROC.png} \# Spatiotemporally Explicit
Networks

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

>>>>

Species interactions are important. It is ultimately interactions
between individuals of different species that drive the structure,
dynamics, and persistence of ecosystems, and the abundance and diversity
of the species within them. Plant-pollinator interactions specifically
drive the function and persistence of ``architecture of biodiversity''
(Bascompte \& Jordano 2007). However, we are far from a robust
understanding of plant-pollinator networks is.

In this paper, we combine several datasets, each spanning several years,
to produce spatially and temporally explicit predictions of
\emph{Bombus} plant-pollinator interactions across the state of
Colorado.

We do this in two parts: (1) metaweb prediction and (2) conditioning our
metaweb prediction on co-occurrence probability.

First, we build a model to predict the metaweb---the network of
\emph{all} interactions, aggregated across all times and spatial
locations---of \emph{Bombus} and wildflower species across Colorado.
(Why do this? The metaweb is more predictable than local interactions.)
We do this using network embedding (\textbf{cite?}). Network embedding
takes each node in the network (either a bumblebee or a wildflower) and
represents it in a latent \(n\) dimensional space. Combination of
running models on Temporal niche (T), Phylogenetic niche (P),
Environmental niche (E), and relative abundance in community (RA).

Second, we then use this metaweb to predict the structure of networks at
specific locations and times of year (Gravel \emph{et al.} 2019).

Finally we suggest a map of sampling priority, which suggests the
locations to sample that will best improve our understanding of the
Colorado \emph{Bombus} pollination metaweb.

@@

We use three separate datasets to estimate the Colorado \emph{Bombus}
metaweb.

@@

\textbf{\emph{Figure 2: Model Fit Figure}}
\includegraphics{./figures/PR_ROC.png}

\hypertarget{spatiotemporally-explicit-networks}{%
\section{Spatiotemporally Explicit
Networks}\label{spatiotemporally-explicit-networks}}

@@

\hypertarget{discussion}{%
\section*{Discussion}\label{discussion}}
\addcontentsline{toc}{section}{Discussion}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Bascompte2007PlaMut}{}%
Bascompte, J. \& Jordano, P. (2007). Plant-Animal Mutualistic Networks:
The Architecture of Biodiversity. \emph{Annual Review of Ecology,
Evolution, and Systematics}, 38, 567--593.

\leavevmode\hypertarget{ref-Gravel2019BriElt}{}%
Gravel, D., Baiser, B., Dunne, J.A., Kopelke, J.-P., Martinez, N.D.,
Nyman, T., \emph{et al.} (2019). Bringing Elton and Grinnell together: A
quantitative framework to represent the biogeography of ecological
interaction networks. \emph{Ecography}, 42, 401--415.

\end{CSLReferences}
